\textbf{International Transport costs:\\New Findings from modeling additive costs}\\Online Appendix (Not for Publication)

### 2021-08-27 redaction/JEGeo/revision_JEGeo/revised_article/DHP_JoEG_rev1.tex
Graphique 9

When aggregating the trade cost measure over the product/country ($i,k$) dimension, \cite{hummels2007} takes the unweighted average value over the $i,k$ dimension, which implicitly attributes a weight equal to 1 to each flow.
Our benchmark specification  (at the root of Figure \ref{fig:totalTC_compeffects_excl}) proceeds differently, as each flow is weighted by its relative value in total trade flows observed in 1974.
In this section, we check whether this difference of treatment is responsible or not for the difference in results relative to the role of the trade composition effects, which we rather attribute to the modeling of the additive component.

@@

\begin{figure}[htbp]
\caption{Transport cost time trends: robustness to the weighting scheme}
\label{fig:compeffects_robustness}
\begin{center}
\includegraphics[height=8cm]
{graph_composition_all_np.pdf}
\end{center}
\end{figure}

@@

\begin{figure}[htbp]
\caption{Transport cost time trends: robustness to the weighting scheme}
\label{fig:comp_IV_SITC5}
\begin{center}
\includegraphics[height=8cm]
{comp_IV_SITC5.pdf}
\end{center}
\end{figure}

>>>>

When aggregating the trade cost measure over the product/country ($i,k$) dimension, \cite{hummels2007} takes the unweighted average value over the $i,k$ dimension, which implicitly attributes a weight equal to 1 to each flow.
Our benchmark specification  (at the root of Figure \ref{fig:totalTC_compeffects_excl}) proceeds differently, as each flow is weighted by its relative value in total trade flows observed in 1974.

----Pas sûr. Je crois que c’est weighted by value/value total for the year --

In this section, we check whether this difference of treatment is responsible or not for the difference in results relative to the role of the trade composition effects, which we rather attribute to the modeling of the additive component.

@@

\begin{figure}[htbp]
\caption{Transport cost time trends: robustness to the weighting scheme}
\label{fig:compeffects_robustness}
\begin{center}
\includegraphics[height=8cm]
{graph_composition_all_np.jpg}
\end{center}
\end{figure}

@@

\begin{figure}[htbp]
\caption{Transport cost time trends: robustness to IV procedure}
\label{fig:comp_IV_SITC5}
\begin{center}
\includegraphics[height=8cm]
{scatter_chronology_baseline_IV_ref1_y_5_3.png}
\end{center}
\end{figure}
